Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-31 tex/Drafts/Draft-3.tex
Intro outline of new sections, n+r+1 composition series

  \vspace{5pt}
  In Section \ref{Crossingless Matchings Section}, we begin by proving Theorem \ref{Irreducibility Theorem}.
  Following this, we prove the existence of a particular filtration with factors given by other crossingless matchings representations;
  using irreducibility, this becomes a composition series.
  This combined with an inductive argument and the branching of Section \ref{Specht Modules Section} allow us to prove Theorem \ref{Correspondence Theorem}.
  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.

  \vspace{5pt}

>>>>

  \vspace{5pt}
  In Section \ref{Crossingless Matchings Section}, we begin by proving proposition \ref{trivial kernel} concerning sign subrepresentations of $M_{2n + r}^r$ when $e \nmid n + r + 1$;
  this allows us to prove Theorem \ref{Irreducibility Theorem}.
  Following this, we prove the existence of a particular filtration with factors given by other crossingless matchings representations;
  using irreducibility, this becomes a composition series.
  This combined with an inductive argument and the branching of Section \ref{Specht Modules Section} allow us to prove Theorem \ref{Correspondence Theorem}.

  \vspace{5pt}
  In Section \ref{Sign section}, we begin by determining an explicit basis for the direct sum $K$ of all sign subrepresentations of $M$ in the case $e = n + r + 1$.
  We prove in Theorem \ref{kernel existence} that such $K$ is nontrivial whe $e = n + r + 1$, and thereby provide an explicit composition series for such $M$ in corrolary \ref{n+r+1 composition series}.
  We finish the section by providing several corollaries concerning the structure of $M_{2n + r}^r$ at irreducible cases with $e < n + r + 1$.
